The effects of varying depth in cosmic shear surveys

### 2019-10-23 paperdraft.tex
typo

For next-generation surveys like Euclid and LSST we have demonstrated that if variable depth in unaccounted for in the analysis, the resulting bias is likely to be significant. A detailed LSST and Euclid study that uses a realistic variation of depth should therefore be conducted. If these studies reach a similar conclusion, variable-depth bias could be circumvented in likelihood analyses by including a cosmology-dependent correction for this effect using the semi-analytical model presented in this paper (see Fig. \ref{fig:comparecosmo}).

>>>>

For next-generation surveys like Euclid and LSST we have demonstrated that if variable depth is unaccounted for in the analysis, the resulting bias is likely to be significant. A detailed LSST and Euclid study that uses a realistic variation of depth should therefore be conducted. If these studies reach a similar conclusion, variable-depth bias could be circumvented in likelihood analyses by including a cosmology-dependent correction for this effect using the semi-analytical model presented in this paper (see Fig. \ref{fig:comparecosmo}).
